Non-word repetition in Yélî Dnye

### 2021-01-12 manuscript.Rmd
further fixing fig 1 and data checks

```{r fig-prevlit, echo = FALSE, ig.pos = "T!", fig.width=8, fig.height=5.5, fig.cap = "NWR scores as a function of age (in years) and item length for comparable studies (1-4 indicating number of syllables, 1=solid, 2=dashed, 3=dotted, 4=dotted and dashed). Arabic data (orange)  from Jaber-Awida (2018); Italian data (black) from Piazzalunga et al. (2019); Tsimane' (green) from Cristia et al. (2020); Yélî Dnye (purple) data from the present study. Central tendency using median in all studies but Jaber-Awida; error using one standard error. Missing points and error bars indicate no or one data point, respectively. Age has been slightly jittered for ease of inspection of different lengths."}

pl<- read.delim("previous_lit.tsv")

@@

@@

for(thislang in levels(pl_stacked$Language)) for(thislength in levels(factor(pl_stacked$Length[pl_stacked$Language== thislang]))){
  myx=pl_stacked$Age[pl_stacked$Language==thislang & pl_stacked$Length==thislength]
  myx=myx+(as.numeric(as.character(thislength))-2)/5 #jitter the length lines a little bit with respect to avg age
  myy=pl_stacked$Median[pl_stacked$Language==thislang & pl_stacked$Length==thislength]
  lines(myy~myx, col=mycols[thislang],lty=as.numeric(thislength)) #join points of same length & lang
  mylb=myy-pl_stacked$se[pl_stacked$Language==thislang & pl_stacked$Length==thislength]
  myhb=myy+pl_stacked$se[pl_stacked$Language==thislang & pl_stacked$Length==thislength]
  for(i in 1:length(mylb)) {
    mylty=as.numeric(as.character(thislength))
    lines(rep(myx[i],2),c(mylb[i],myhb[i]),col=mycols[thislang],lty=mylty) #error bar
    lines(c(myx[i]-.1,myx[i]+.1),c(mylb[i],mylb[i]),col=mycols[thislang],lty=mylty) #lower error bar tip
    lines(c(myx[i]-.1,myx[i]+.1),c(myhb[i],myhb[i]),col=mycols[thislang],lty=mylty) #higher error bar tip
    }
}

@@

Our final exploratory analysis assessed whether variation in scores was structured by factors that vary across individuals. As shown in Figure \@ref(fig:Fig2-scores-by-age), there was a greater deal of variance across the tested age range, with significantly higher NWR scores for older children (Spearman's rank correlation, given inequality of variance, rho (`r corage$statistic`) = `r corage$estimate`, p `r pval.display(corage$p.value)`). In contrast, there was no clear association between NWR scores and sex (Welch t (`r tsex$parameter`) = `r tsex$statistic`, p `r pval.display(tsex$p.value)`), birth order  (data missing for `r sum(is.na(demo$birthOrder[demo$included=="yes"]))` children, rho = (`r round(corbo$statistic,1)`) = `r corbo$estimate`, p `r pval.display(corbo$p.value)`), or maternal education  (data missing for `r sum(is.na(demo$matEd[demo$included=="yes"]))` children,  rho ( `r round(corme$statistic,1)`) = `r corme$estimate`, p `r pval.display(corme$p.value)`).

>>>>

```{r fig-prevlit, echo = FALSE, ig.pos = "T!", fig.width=8, fig.height=5.5, fig.cap = "NWR scores as a function of age (in years) and item length for comparable studies (1-4 indicating number of syllables, 1=solid, 2=dashed, 3=dotted, 4=dotted and dashed). Jaber-Awida (2018) reported on 20 Arabic learners (orange); Piazzalunga et al. (2019) reported on groups of 24-60 Italian learners (black); Cristia et al. (2020) reported on groups of 4-6 Tsimane' learners (green); the present study reports on groups of 8-19 Yélî Dnye learners (purple). Central tendency is mean in Arabic and Tsimane', median in Italian and Yélî Dnye; error is one standard error. Age has been slightly jittered for ease of inspection of different lengths at a given age."}

pl<- read.csv("previous_lit.csv")

@@

mywd = c( 
             "Arabic" = 1,
             "Italian"   =1,
             "Tsimane'" = 1,
             "Yélî Dnye" = 2)

@@

for(thislang in levels(pl_stacked$Language)) for(thislength in levels(factor(pl_stacked$Length[pl_stacked$Language== thislang]))){
  myx=pl_stacked$Age[pl_stacked$Language==thislang & pl_stacked$Length==thislength]
  myx=myx+(as.numeric(as.character(thislength))-2)/5 #jitter the length lines a little bit with respect to avg age
  myy=pl_stacked$Median[pl_stacked$Language==thislang & pl_stacked$Length==thislength]
  lines(myy~myx, col=mycols[thislang],lty=as.numeric(thislength),lwd=mywd[thislang]) #join points of same length & lang
  mylb=myy-pl_stacked$se[pl_stacked$Language==thislang & pl_stacked$Length==thislength]
  myhb=myy+pl_stacked$se[pl_stacked$Language==thislang & pl_stacked$Length==thislength]
  for(i in 1:length(mylb)) {
    mylty=as.numeric(as.character(thislength))
    lines(rep(myx[i],2),c(mylb[i],myhb[i]),col=mycols[thislang],lty=mylty) #error bar
    lines(c(myx[i]-.1,myx[i]+.1),c(mylb[i],mylb[i]),col=mycols[thislang],lty=mylty) #lower error bar tip
    lines(c(myx[i]-.1,myx[i]+.1),c(myhb[i],myhb[i]),col=mycols[thislang],lty=mylty) #higher error bar tip
    }
}

@@

Our final exploratory analysis assessed whether variation in scores was structured by factors that vary across individuals. As shown in Figure \@ref(fig:Fig2-scores-by-age), there was a greater deal of variance across the tested age range, with significantly higher NWR scores for older children (Spearman's rank correlation, given inequality of variance, rho (`r corage$statistic`) = `r corage$estimate`, p `r pval.display(corage$p.value)`). In contrast, there was no clear association between NWR scores and sex (Welch t (`r tsex$parameter`) = `r tsex$statistic`, p `r pval.display(tsex$p.value)`), birth order  (data missing for `r sum(is.na(demo$birthOrder[demo$included=="yes"]))` children, rho = (`r round(corbo$statistic,1)`) = `r corbo$estimate`, p `r pval.display(corbo$p.value)`), or maternal education  (rho ( `r round(corme$statistic,1)`) = `r corme$estimate`, p `r pval.display(corme$p.value)`).

### 2021-01-12 manuscript.tex
further fixing fig 1 and data checks

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/fig-prevlit-1.pdf}
\caption{\label{fig:fig-prevlit}NWR scores as a function of age (in years) and item length for comparable studies (1-4 indicating number of syllables, 1=solid, 2=dashed, 3=dotted, 4=dotted and dashed). Arabic data (orange) from Jaber-Awida (2018); Italian data (black) from Piazzalunga et al. (2019); Tsimane' (green) from Cristia et al. (2020); Yélî Dnye (purple) data from the present study. Central tendency using median in all studies but Jaber-Awida; error using one standard error. Missing points and error bars indicate no or one data point, respectively. Age has been slightly jittered for ease of inspection of different lengths.}
\end{figure}

@@

Our final exploratory analysis assessed whether variation in scores was structured by factors that vary across individuals. As shown in Figure \ref{fig:Fig2-scores-by-age}, there was a greater deal of variance across the tested age range, with significantly higher NWR scores for older children (Spearman's rank correlation, given inequality of variance, rho (6,014.70) = 0.44, p \textless{} 0.01). In contrast, there was no clear association between NWR scores and sex (Welch t (27.56) = -0.29, p = 0.77), birth order (data missing for 15 children, rho = (3,441.90) = -0.18, p = 0.39), or maternal education (data missing for 0 children, rho ( 9,594.40) = 0.10, p = 0.54).

>>>>

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/fig-prevlit-1.pdf}
\caption{\label{fig:fig-prevlit}NWR scores as a function of age (in years) and item length for comparable studies (1-4 indicating number of syllables, 1=solid, 2=dashed, 3=dotted, 4=dotted and dashed). Jaber-Awida (2018) reported on 20 Arabic learners (orange); Piazzalunga et al. (2019) reported on groups of 24-60 Italian learners (black); Cristia et al. (2020) reported on groups of 4-6 Tsimane' learners (green); the present study reports on groups of 8-19 Yélî Dnye learners (purple). Central tendency is mean in Arabic and Tsimane', median in Italian and Yélî Dnye; error is one standard error. Age has been slightly jittered for ease of inspection of different lengths at a given age.}
\end{figure}

@@

Our final exploratory analysis assessed whether variation in scores was structured by factors that vary across individuals. As shown in Figure \ref{fig:Fig2-scores-by-age}, there was a greater deal of variance across the tested age range, with significantly higher NWR scores for older children (Spearman's rank correlation, given inequality of variance, rho (6,014.70) = 0.44, p \textless{} 0.01). In contrast, there was no clear association between NWR scores and sex (Welch t (27.56) = -0.29, p = 0.77), birth order (data missing for 15 children, rho = (3,441.90) = -0.18, p = 0.39), or maternal education (rho ( 9,594.40) = 0.10, p = 0.54).
